DATA 607 Project 1 - Chess Scores

### 2018-09-16 DATA607/Project_1.Rmd
More work on Project 1

```{r add_averages}
player_df <- merge(player_df, averages) %>%
  mutate(average_opponent_pre_rating = as.integer(average)) %>%
    select(-player_id, -average)
```

@@

```{r view_player_df_2}
head(player_df)
```

@@

>>>>

```{r add_averages}
df <- merge(player_df, averages) %>%
  mutate(average_opponent_pre_rating = as.integer(average)) %>%
    select(-player_id, -average)
```

@@

```{r view_df}
head(df)
```

@@

## Fun with the Data

I really enjoy graph theory and couldn't pass up the oportunity to create a network graph from this chess data and visualize it.  I will use the igraph library to do that.  This is beyond the scope of the project and is for the fun of it.

```{r}
library(igraph)
G <- matches %>%
  select(player_id, opponent) %>%
  graph_from_data_frame(., directed = FALSE)

nodes <- data.frame(V(G)$name) %>%
  rename(player_id = V.G..name) %>%
  merge(player_df) %>%
  select(player_id, players_name)

par(oma=c(0, 0, 0, 0))
par(mar=c(0, 0, 0, 0))
#par(pin=c(3, 3)) 
#plot(G, layout = layout_with_fr(G))
plot(G, layout = layout_with_graphopt(G))
#G$layout <- layout_in_circle
#plot(G)
```
